Shoemaker et al, 2015: An Ultrasensitive Mechanism Regulates Influenza Virus-Induced Inflammation

### 2019-02-11 scripts/shoemaker2015.Rmd
MAINT Adding TODO list

# Clustering
filter_genes = FALSE
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

```{r}
# Normalize
data_set = EDASeq::newSeqExpressionSet(as.matrix(data), phenoData=meta)
data_normalized = EDASeq::betweenLaneNormalization(
    data_set, which="upper", offset=TRUE, round=FALSE)
data_normalized = EDASeq::normCounts(data_normalized)
```

@@

```{r}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrast_formula,
	levels=levels(meta$Group))
    model = edgeWithContrasts(as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval
    de_analysis[contrast_name_qval] = model$qval
}
```

@@

@@

# FIXME should use a package with a smarter initialization
kmeans_clusters = kmeans(rescaled_fitted_data, n_clusters, nstart=10)
all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
    scores = score_genes_centroid(data, kmeans_clusters$centers[k,])
    all_scores[paste0("cluster_", k)] = scores
}

>>>>

# Clustering
filter_genes = TRUE
n_genes_to_keep = 5000
n_clusters = 20
percentage_genes_to_label = 0.5
```

@@

FIXME this is not the normalization to use (this is the one for the EPICON
data)
```{r}
# Normalize
data_set = EDASeq::newSeqExpressionSet(as.matrix(data), phenoData=meta)
data_normalized = EDASeq::betweenLaneNormalization(
    data_set, which="upper", offset=TRUE, round=FALSE)
data_normalized = EDASeq::normCounts(data_normalized)
```

@@

FIXME add estimation of log fold change.

```{r}
# Define contrast
de_analysis = data.frame(row.names=row.names(data))
for(contrast_formula in timecourse_contrasts){
    contrast = limma::makeContrasts(
	contrast_formula,
	levels=levels(meta$Group))
    model = edgeWithContrasts(as.matrix(data), meta, contrast)
    contrast_name = gsub(" ", "", contrast_formula, fixed=TRUE)
    contrast_name_pval = paste(contrast_name, "-pval", sep="")
    contrast_name_qval = paste(contrast_name, "-qval", sep="")
    de_analysis[contrast_name_pval] = model$pval
    de_analysis[contrast_name_qval] = model$qval
}

pvalues = de_analysis
```

@@

FIXME should use a package with a smarter initialization (kmeans++)

@@

kmeans_clusters = kmeans(rescaled_fitted_data, n_clusters, nstart=10)
all_scores = data.frame(row.names=row.names(data))
for(k in 1:n_clusters){
    scores = score_genes_centroid(data, kmeans_clusters$centers[k,])
    all_scores[paste0("cluster_", k)] = scores
}
